---
title: "Choosing replications"
author: "Amy Heather"
date: "`r Sys.Date()`"
output:
  github_document:
      toc: true
      html_preview: false
---

This notebook documents the choice of the number of replications.

The generated images are saved and then loaded, so that we view the image as saved (i.e. with the dimensions set in `ggsave()`). This also avoids the creation of a `_files/` directory when knitting the document (which would save all previewed images into that folder also, so they can be rendered and displayed within the output `.md` file, even if we had not specifically saved them). These are viewed using `include_graphics()`, which must be the last command in the cell (or last in the plotting function).

The run time is provided at the end of the notebook.

## Set up

Install the latest version of the local simulation package. If running sequentially, `devtools::load_all()` is sufficient. If running in parallel, you must use `devtools::install()`.

```{r}
devtools::load_all()
```

Load required packages.

```{r}
# nolint start: undesirable_function_linter.
library(data.table)
library(dplyr)
library(knitr)
library(simulation)
library(tidyr)

options(data.table.summarise.inform = FALSE)
options(dplyr.summarise.inform = FALSE)
# nolint end
```

Start timer.

```{r}
start_time <- Sys.time()
```

Define path to outputs folder.

```{r}
output_dir <- file.path("..", "outputs")
```

## Choosing the number of replications

The **confidence interval method** can be used to select the number of replications to run. The more replications you run, the narrower your confidence interval becomes, leading to a more precise estimate of the model's mean performance.

First, you select a desired confidence interval - for example, 95%. Then, run the model with an increasing number of replications, and identify the number required to achieve that precision in the estimate of a given metric - and also, to maintain that precision (as the intervals may converge or expand again later on).

This method is less useful for values very close to zero - so, for example, when using utilisation (which ranges from 0 to 1) it is recommended to multiple values by 100.

When selecting the number of replications you should repeat the analysis for all performance measures and select the highest value as your number of replications.

It's important to check ahead, to check that the 5% precision is maintained - which is fine in this case - it doesn't go back up to future deviation.

```{r}
path <- file.path(output_dir, "choose_param_conf_int_1.png")

# Run calculations and produce plot
ci_df <- confidence_interval_method(
  replications = 150L,
  desired_precision = 0.05,
  metric = "mean_serve_time_nurse",
  yaxis_title = "Mean time with nurse",
  path = path,
  min_rep = 98L
)

# Preview dataframe
head(ci_df)

# View first ten rows were percentage deviation is below 5
ci_df %>%
  filter(perc_deviation < 5L) %>%
  head(10L)

# View plot
include_graphics(path)
```

It is also important to check across multiple metrics.

```{r}
path <- file.path(output_dir, "choose_param_conf_int_3.png")

# Run calculations and produce plot
ci_df <- confidence_interval_method(
  replications = 200L,
  desired_precision = 0.05,
  metric = "utilisation_nurse",
  yaxis_title = "Mean nurse utilisation",
  path = path,
  min_rep = 148L
)

# View first ten rows were percentage deviation is below 5
ci_df %>%
  filter(perc_deviation < 5L) %>%
  head(10L)

# View plot
include_graphics(path)
```

## Automated detection of the number of replications

Run the algorithm (which will run model with increasing reps) for a few different metrics.

```{r}
# Set up and run algorithm
alg <- ReplicationsAlgorithm$new(param = parameters())
alg$select()

# View results
alg$nreps
alg$summary_table
```

## Run time

```{r end_timer}
# Get run time in seconds
end_time <- Sys.time()
runtime <- as.numeric(end_time - start_time, units = "secs")

# Display converted to minutes and seconds
minutes <- as.integer(runtime / 60L)
seconds <- as.integer(runtime %% 60L)
cat(sprintf("Notebook run time: %dm %ds", minutes, seconds))
```
