---
title: "Analysis"
output: html_document
---

To knit this vignette, will first need to run `devtools::install()` to fetch the latest version of our `simulation` model code.

## Set up

Import required packages.

```{r}
# nolint start: undesirable_function_linter.
library(dplyr, warn.conflicts = FALSE)
library(ggplot2)
library(simmer, warn.conflicts = FALSE)
library(simulation)

options(dplyr.summarise.inform = FALSE)
# nolint end
```

Start timer.

```{r}
start_time <- Sys.time()
```

Define path to outputs folder.

```{r}
output_dir <- file.path("..", "outputs")
```

## Default run

Run with default parameters.

```{r}
envs <- trial(param = defaults())
```

Process results and save to `.csv`.

```{r}
trial_results <- process_replications(envs)
head(trial_results)

write.csv(trial_results, file.path(output_dir, "base_trial.csv"))
```

## View spread of results across replication

```{r}
#' Plot spread of results from across replications, for chosen column.
#'
#' Generate figure, show it, and then save under specified file name.
#'
#' @param column Name of column to plot.
#' @param x_label X axis label.
#' @param file Filename to save figure to.

plot_results_spread <- function(column, x_label, file) {

  # Generate plot
  p <- ggplot(trial_results, aes(.data[[column]])) +
    geom_histogram(bins = 10L) +
    labs(x = x_label, y = "Frequency") +
    theme_minimal()

  # Show plot
  print(p)

  # Save plot
  ggsave(filename = file.path(output_dir, file), width = 6.5, height = 4L)
}
```

```{r}
plot_results_spread(column = "arrivals",
                    x_label = "Arrivals",
                    file = "spread_arrivals.png")

plot_results_spread(column = "mean_waiting_time_nurse",
                    x_label = "Mean wait time for nurse",
                    file = "spread_nurse_wait.png")

plot_results_spread(column = "mean_activity_time_nurse",
                    x_label = "Mean length of nurse consultation",
                    file = "spread_nurse_time.png")

plot_results_spread(column = "utilisation_nurse",
                    x_label = "Mean nurse utilisation",
                    file = "spread_nurse_util.png")
```

## Scenario analysis

```{r}
#' Run a set of scenarios
#'
#' @param scenarios List where key is name of parameter and value is a list of
#' different values to run in scenarios
#'
#' @return Tibble with results from each replication for each scenario.

run_scenarios <- function(scenarions) {
  # Generate all permutations of the scenarios
  all_scenarios <- expand.grid(scenarios)

  # Preview the number of scenarios
  print(sprintf("There are %d scenarios. Running:", nrow(all_scenarios)))

  results <- list()

  # Iterate through each scenario
  for (index in seq_len(nrow(all_scenarios))) {

    # Filter to one of the scenarios
    scenario_to_run <- all_scenarios[index, ]

    # Print the scenario parameters
    formatted_scenario <- toString(
      paste0(names(scenario_to_run), " = ", scenario_to_run)
    )
    print(paste0("Scenario: ", formatted_scenario))

    # Overwrite defaults with scenario-specific values
    param <- defaults()
    param[["scenario_name"]] <- index
    for (key in names(scenario_to_run)) {
      param[[key]] <- scenario_to_run[[key]]
    }

    # Run the trial for the current scenario
    envs <- trial(param)

    # Extract results
    scenario_result <- process_replications(envs)

    # Append scenario parameters to the results
    scenario_result[["scenario"]] <- index
    for (key in names(scenario_to_run)) {
      scenario_result[[key]] <- scenario_to_run[[key]]
    }

    # Append to results list
    results[[index]] <- scenario_result
  }
  return(do.call(rbind, results))
}
```

```{r}
# Run scenario analysis
scenarios <- list(
  patient_inter = c(3L, 4L, 5L, 6L, 7L),
  number_of_nurses = c(5L, 6L, 7L, 8L)
)

scenario_results <- run_scenarios(scenarios)
```

```{r}
# Preview scenario results dataframe
print(dim(scenario_results))
head(scenario_results)
```

Example plot

```{r}
#' Plot results from different model scenarios.
#'
#' @param results Dataframe with results from each replication of scenarios.
#' @param x_var Name of variable to plot on X axis.
#' @param result_var Name of variable with results, to plot on Y axis.
#' @param colour_var Name of variable to colour lines with (or set to NULL).
#' @param xaxis_title Title for X axis.
#' @param yaxis_title Title for Y axis.
#' @param legend_title Title for figure legend.
#' @param file Filename to save figure to.

plot_scenario <- function(results, x_var, result_var, colour_var, xaxis_title,
                          yaxis_title, legend_title, file) {
  # If x_var and colour_var are provided, combine both in a list to use
  # as grouping variables when calculating average results
  if (!is.null(colour_var)) {
    group_vars <- c(x_var, colour_var)
  } else {
    group_vars <- c(x_var)
  }

  # Calculate average results from each scenario
  df <- scenario_results %>%
    group_by_at(group_vars) %>%
    summarise(mean = mean(.data[[result_var]]),
              std_dev = sd(.data[[result_var]]),
              ci_lower = t.test(.data[[result_var]])[["conf.int"]][[1L]],
              ci_upper = t.test(.data[[result_var]])[["conf.int"]][[2L]])

  # Generate plot - with or without colour, depending on whether it was given
  if (!is.null(colour_var)) {
    # Convert colour variable to factor so it is treated like categorical
    df[[colour_var]] <- as.factor(df[[colour_var]])
    # Create plot
    p <- ggplot(df, aes(x = .data[[x_var]], y = mean,
                        group = .data[[colour_var]])) +
      geom_line(aes(color = .data[[colour_var]])) +
      geom_ribbon(aes(ymin = .data[["ci_lower"]], ymax = .data[["ci_upper"]],
                      fill = .data[[colour_var]]), alpha = 0.1)
  } else {
    # Create plot
    p <- ggplot(df, aes(x = .data[[x_var]], y = mean)) +
      geom_line() +
      geom_ribbon(aes(ymin = .data[["ci_lower"]], ymax = .data[["ci_upper"]]),
                  alpha = 0.1)
  }

  # Modify labels and style
  p <- p +
    labs(x = xaxis_title, y = yaxis_title, color = legend_title,
         fill = legend_title) +
    theme_minimal()

  # Show plot
  print(p)

  # Save plot
  ggsave(filename = file.path(output_dir, file), width = 6.5, height = 4L)
}
```

```{r}
plot_scenario(
  results = scenario_results,
  x_var = "patient_inter",
  result_var = "mean_waiting_time_nurse",
  colour_var = "number_of_nurses",
  xaxis_title = "Patient inter-arrival time",
  yaxis_title = "Mean wait time for nurse (minutes)",
  legend_title = "Nurses",
  file = "scenario_nurse_wait.png"
)

plot_scenario(
  results = scenario_results,
  x_var = "patient_inter",
  result_var = "utilisation_nurse",
  colour_var = "number_of_nurses",
  xaxis_title = "Patient inter-arrival time",
  yaxis_title = "Mean nurse utilisation",
  legend_title = "Nurses",
  file = "scenario_nurse_util.png"
)

# TODO: Why do these confidence intervals look much wider than in Python?
```

Example table.

## Sensitivity analysis

```{r}
# TODO: Add sensitivity analysis
```

## Calculate run time

```{r end_timer}
# Get run time in seconds
end_time <- Sys.time()
runtime <- as.numeric(end_time - start_time, units = "secs")

# Display converted to minutes and seconds
minutes <- as.integer(runtime / 60L)
seconds <- as.integer(runtime %% 60L)
print(sprintf("Notebook run time: %dm %ds", minutes, seconds))
```
